Appendix S1: Supporting Information

### 2021-09-06 ms/SI.Rmd
Fix SI K plot and bioregions plot

```{r k-plot, fig.width = 7, fig.height = 3}
a <- k_taxonomy$df %>%
  as_tibble() %>%
  mutate(
    optimal_auto = ifelse(k == k_taxonomy$optimal$k, TRUE, FALSE),
    label = ifelse(k == k_taxonomy$optimal$k, glue::glue("k = {k}"), "")
  ) %>%
  ggplot(aes(x = k, y = ev)) +
  geom_path() +
  geom_point(aes(color = optimal_auto), size = 2.5) +
  geom_text(aes(label = label), vjust = 0, nudge_y = 0.02, size = 4) +
  scale_color_manual(values = c("TRUE" = "#E31A1C", "FALSE" = "black")) +
  labs(
    y = "Explained variance",
    x = "Number of clusters") +
  theme(
    legend.position = "none"
  )

@@

b <- k_phylogeny$df %>%
  as_tibble() %>%
  mutate(
    optimal_auto = ifelse(k == k_phylogeny$optimal$k, TRUE, FALSE),
    label = ifelse(k == k_phylogeny$optimal$k, glue::glue("k = {k}"), "")
  ) %>%
  ggplot(aes(x = k, y = ev)) +
  geom_path() +
  geom_point(aes(color = optimal_auto), size = 2.5) +
  geom_text(aes(label = label), vjust = 0, nudge_y = 0.02, size = 4) +
  scale_color_manual(values = c("TRUE" = "#E31A1C", "FALSE" = "black")) +
  labs(
    y = "Explained variance",
    x = "Number of clusters") +
  theme(
    legend.position = "none"
  )

@@

**`r s_figure("k-plot")`**. Selection of *k* for bioregions. (a), taxonomic bioregions. (b), phylogenetic bioregions. Color indicates optimal *k* selected selected by the `r func("optimal_phyloregion")` function in the R package `r pack("phyloregion")` (black, non-optimal; red, optimal; see Methods).

@@

```{r bioregions-env, fig.width = 7, fig.height = 5}
# Make pot showing bioregions by temperature and precipitation
a <-
  ggplot(biodiv_ferns_spatial_lumped, aes(x = precip, y = temp, color = taxonomic_cluster)) +
  geom_point(size = 1, alpha = 0.7) +
  scale_color_manual(values = bioregion_cols) +
  scale_y_continuous(labels = function(x) x/10) +
  labs(y = "Temperature (°C)", x = "Precipitation (mm)", color = "Cluster", subtitle = "Taxonomic bioregions") +
  theme(legend.position = "bottom")

b <-
  ggplot(biodiv_ferns_spatial_lumped, aes(x = precip, y = temp, color = phylo_cluster)) +
  geom_point(size = 1, alpha = 0.7) +
  scale_color_manual(values = bioregion_cols) +
  scale_y_continuous(labels = function(x) x/10) +
  labs(y = "Temperature (°C)", x = "Precipitation (mm)", color = "Cluster", subtitle = "Phylogenetic bioregions") +
  theme(legend.position = "bottom")

@@

**`r s_figure("bioregions-env")`**. Scatterplots of grid cell membership in (a) taxonomic or (b) phylogenetic bioregions arranged by mean annual temperature and annual precipitation. Points shown with partial transparency; darker areas indicate overlapping points. Bioregions with three or fewer grid-cells are lumped into the "Other" category.

>>>>

```{r k-plot, fig.width = 7, fig.height = 3}
a <- k_taxonomy$df %>%
  as_tibble() %>%
  mutate(
    optimal_auto = ifelse(k == k_taxonomy$optimal$k, TRUE, FALSE),
    label = ifelse(k == k_taxonomy$optimal$k, glue::glue("k = {k}"), "")
  ) %>%
  ggplot(aes(x = k, y = ev)) +
  geom_path() +
  geom_point(aes(color = optimal_auto), size = 2.5) +
  geom_text(aes(label = label), vjust = 0, nudge_y = 0.02, size = 4) +
  scale_color_manual(values = c("TRUE" = "#E31A1C", "FALSE" = "black")) +
  scale_y_continuous(expand = expansion(add = c(0.025,0.05))) +
  scale_x_continuous(breaks = c(2,4,6,8,10)) +
  labs(
    y = "Explained variance",
    x = "Number of clusters") +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank()
  )

@@

b <- k_phylogeny$df %>%
  as_tibble() %>%
  mutate(
    optimal_auto = ifelse(k == k_phylogeny$optimal$k, TRUE, FALSE),
    label = ifelse(k == k_phylogeny$optimal$k, glue::glue("k = {k}"), "")
  ) %>%
  ggplot(aes(x = k, y = ev)) +
  geom_path() +
  geom_point(aes(color = optimal_auto), size = 2.5) +
  geom_text(aes(label = label), vjust = 0, nudge_y = 0.02, size = 4) +
  scale_color_manual(values = c("TRUE" = "#E31A1C", "FALSE" = "black")) +
  scale_y_continuous(expand = expansion(add = c(0.025,0.05))) +
  scale_x_continuous(breaks = c(2,4,6,8,10)) +
  labs(
    y = "Explained variance",
    x = "Number of clusters") +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank()
  )

@@

**`r s_figure("k-plot")`**. Selection of *k* for bioregions. (a), taxonomic bioregions. (b), phylogenetic bioregions. Color indicates optimal *k* selected selected by the `r func("optimal_phyloregion")` function in the R package `r pack("phyloregion")` (black, non-optimal; red, optimal).

@@

```{r bioregions-env, fig.width = 7, fig.height = 5}
# Make pot showing bioregions by temperature and precipitation
a <-
  ggplot(biodiv_ferns_spatial_lumped, aes(x = precip, y = temp, color = taxonomic_cluster)) +
  geom_point(size = 1, alpha = 0.7) +
  scale_color_manual(
    values = bioregion_cols,
    guide = guide_legend(
      direction = "horizontal",
      title.position = "top",
      label.position = "left")
  ) +
  scale_y_continuous(labels = function(x) x/10) +
  labs(y = "Temperature (°C)", x = "Precipitation (mm)", color = "Bioregion", subtitle = "Taxonomic bioregions") +
  theme(legend.position = "bottom")

b <-
  ggplot(biodiv_ferns_spatial_lumped, aes(x = precip, y = temp, color = phylo_cluster)) +
  geom_point(size = 1, alpha = 0.7) +
  scale_color_manual(
    values = bioregion_cols,
    guide = guide_legend(
      direction = "horizontal",
      title.position = "top",
      label.position = "left")) +
  scale_y_continuous(labels = function(x) x/10) +
  labs(y = "Temperature (°C)", x = "Precipitation (mm)", color = "Bioregion", subtitle = "Phylogenetic bioregions") +
  theme(legend.position = "bottom")

@@

**`r s_figure("bioregions-env")`**. Scatterplots of grid cell membership in (a) taxonomic or (b) phylogenetic bioregions arranged by mean annual temperature and annual precipitation. Points shown with partial transparency; darker areas indicate overlapping points. Bioregions not consisting of > 1 grid-cell each are lumped into the "Other" category.
